Ecuador plant species BIEN occurrence cleaning

### 2022-12-02 code/L1/L1_Ecuador_plants_BIEN_occ.Rmd
Rename L1_Ecuador_plants_BIEN.Rmd to L1_Ecuador_plants_BIEN_occ.Rmd

---
title: "Ecuador plant species BIEN trait cleaning"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "Ecuador_BIEN_traits.csv"
data output: "TBD"
project: "Frugivoria"
date: "2022-10-10"
output: html_document
---

@@

# Read in BIEN trait data
```{r}
database <- read.csv(file.path(data_path, "Ecuador_BIEN_traits.csv"))
```

# Configure BIEN trait data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"configuration table.csv"))

@@

# Save output data to csv
```{r}
# Export the data into a CSV file
ecuador_BIEN_plant_traits_cleaned_path <- file.path(output_path,"Ecuador_BIEN_plant_traits_cleaned.csv")
write.csv(output, file = ecuador_BIEN_plant_traits_cleaned_path)
ecuador_BIEN_plant_traits_unresolved_path <- file.path(output_path,"Ecuador_BIEN_plant_traits_unresolved.csv")
write.csv(unresolved_names, file = ecuador_BIEN_plant_traits_unresolved_path)
```

>>>>

---
title: "Ecuador plant species BIEN occurrence cleaning"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "Ecuador_BIEN_occurrence.csv"
data output: "Ecuador_BIEN_plant_occ_cleaned.csv", "Ecuador_BIEN_plant_occ_unresolved.csv"
project: "Frugivoria"
date: "2022-10-10"
output: html_document
---

@@

# Read in BIEN occ data
```{r}
database <- read.csv(file.path(data_path,"Ecuador_BIEN_occurrence.csv"))
```

# Configure BIEN data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"configuration table.csv"))

@@

# Save output data to csv
```{r}
# Export the data into a CSV file
ecuador_BIEN_plant_occ_cleaned_path <- file.path(output_path,"Ecuador_BIEN_plant_occ_cleaned.csv")
write.csv(output, file = ecuador_BIEN_plant_occ_cleaned_path)
ecuador_BIEN_plant_occ_unresolved_path <- file.path(output_path,"Ecuador_BIEN_plant_occ_unresolved.csv")
write.csv(unresolved_names, file = ecuador_BIEN_plant_occ_unresolved_path)
```
